---
title: "Ex3"
output: github_document
---


```{r}
setwd("C:\\Users\\Ben\\Documents\\R\\Ex3")
```

###Twitter API
This is R code to get twitter data using their API
```{r}
#install.packages("devtools")
#devtools::install_github("mkearney/rtweet")
library(rtweet)
appname <- "AppName"
consumerKey <- "myKey"
consumerSecret <- "mySecretKey"
#twitter_token <- create_token(
#    app = appname,
#    consumer_key = consumerKey,
#    consumer_secret = consumerSecret)
mk <- as.data.frame(read.csv("mk_id.csv",colClasses = 'character'))
mk_follow <- NA
j <-0 
for(i in mk$id){
  follows <- get_friends(i,parse = T)
  mk_follow[j+1] <- follows
  j <- j+1
}
```
We used python to get our data
here is code: 
https://github.com/BenEfrati/ex1/blob/master/network%20analysis/init.py

The id is the twitter user id of MKs (Members of Knesset)
The edges in the graph are friends of each user
and the vertices are the MKs.
```{r}
library(igraph)

md_name <- as.data.frame(read.csv('mk_id.csv',colClasses = 'character'))
data_mk <- as.data.frame(read.csv('friends.csv',colClasses = 'character'))
new <- data_mk
new[] <- md_name$name[match(unlist(data_mk), md_name$id)]
new <- na.omit(new)
twitterg <- graph.data.frame(new, directed = F)
degr.score <- degree(twitterg)
V(twitterg)$size <- degr.score/15
V(twitterg)$name <- ifelse(V(twitterg)$size>10,V(twitterg)$name,NA)
#twitterg$layout <- layout.fruchterman.reingold(twitterg, niter=5000)
igraph.options(plot.layout=layout.graphopt, vertex.size=7)

plot(twitterg, asp=0)

#restore names and sizes
twitterg <- graph.data.frame(new, directed = F)
```

##Centrality

###Compute betweenes
```{r}
library(igraph)
between <- betweenness(twitterg)
maxBetweenes <- which.max(between)
cat("The actor with the maximum betweenes is:\n")
maxBetweenes

```

###Compute Closeness
```{r}
library(igraph)
close <- closeness(twitterg)
maxCloseness <- which.max(close)
cat("The actor with the maximum closeness is:\n")
maxCloseness

```

###Compute Closeness
```{r}
library(igraph)
eigen <- eigen_centrality(twitterg, directed = F)
maxEigen <- which.max(eigen$vector)
cat("The actor with the maximum eigenvector is:\n")
maxEigen

```

##Communities
###First algorithm 
cluster_edge_betweenness performs this algorithm by calculating the edge betweenness of the graph, removing the edge with the highest edge betweenness score, then recalculating edge betweenness of the edges and again removing the one with the highest score, etc.
```{r}
set.seed(123)
tgc <- cluster_edge_betweenness(twitterg,directed = F)
print("Number of communities:")
print(length(tgc))
print("Size of communities:")
print(sizes(tgc))
print("Modularity is:")
print(modularity(tgc))
plot(tgc,twitterg)

```
###Second algorithm 
```{r}
set.seed(123)
tgreedy <- cluster_leading_eigen(twitterg)
print("Number of communities:")
print(length(tgreedy))
print("Size of communities:")
print(sizes(tgreedy))
print("Modularity is:")
print(modularity(tgreedy))
plot(tgreedy,twitterg)

```
